### 2023-05-11 paper.tex
new version

\newcommand{\cncoverheader}{
  \noindent\begin{tikzpicture}[remember picture, overlay]
    \begin{scope}[shift={(0,-20mm)}]
      \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=20mm]{example-image-a}};
      \node[anchor=south,inner sep=0mm] at (\textwidth/2, 5mm) {\includegraphics[height=10mm]{example-image-b}};
      \node[anchor=south east, inner sep=0mm] at (\textwidth, 9mm) {\includegraphics[height=12mm]{example-image-c}};
      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 6mm) {\footnotesize ISSN \issn};
      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 1.5mm) {\bf\footnotesize OPEN~\includegraphics[width=6px]{images/open-access.eps}~ACCESS};

@@

\newcommand{\cncoverfooter}{
  \noindent\begin{tikzpicture}[remember picture, overlay]
    \begin{scope}[shift={(0,0)}]
      \draw[line width=1pt, cncolor] (0, 0) -- (\textwidth, 0);
      \node[anchor=north west,inner sep=0mm] at (0, -1.5mm) {\includegraphics[height=8mm]{example-image-a}};
      \node[anchor=west, inner sep=0mm] at (15mm, -5.6mm) {\footnotesize Published by Ciência e Natura under a CC BY-NC-SA 4.0 license.};
    \end{scope}
  \end{tikzpicture}
 \par\vspace{24mm}
}

>>>>

\newcommand{\cncoverheader}{
  \noindent\begin{tikzpicture}[remember picture, overlay]
    \begin{scope}[shift={(0,-20mm)}]
      \node[anchor=south west,inner sep=0mm] at (0, 0) {\includegraphics[height=25mm]{images/logo-ufsm.png}};
      \node[anchor=south,inner sep=0mm] at (\textwidth/2, 7mm) {\includegraphics[height=16mm]{images/logo-ciencia-e-natura.jpg}};
      \node[anchor=south east, inner sep=0mm] at (\textwidth, 9mm) {\includegraphics[height=17mm]{images/revista.jpg}};
      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 6mm) {\footnotesize ISSN \issn};
      \node[left, anchor=east, inner sep = 0mm] at (\textwidth, 1.5mm) {\bf\footnotesize OPEN~\includegraphics[width=6px]{images/open-access.eps}~ACCESS};

@@

\newcommand{\cncoverfooter}{
  \noindent\begin{tikzpicture}[remember picture, overlay]
    \begin{scope}[shift={(0,0)}]
      \draw[line width=1pt, cncolor] (0, 0) -- (\textwidth, 0);
      \node[anchor=north west,inner sep=0mm] at (0, -1.5mm) {\includegraphics[height=6.5mm]{images/creativecommons.png}};
      \node[anchor=west, inner sep=0mm] at (20mm, -5.0mm) {\footnotesize Published by Ciência e Natura under a CC BY-NC-SA 4.0 license.};
    \end{scope}
  \end{tikzpicture}
 \par\vspace{10mm}
}
